---
title: "Markdown MS"
author: ["Christina Bonsell", "Nathan McTigue", "Emily Bristol", "Marilyn Monroe"]
date: "October 11, 2019"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=F, warning=F, message=F}
library(ggplot2)
library(knitr)
library(broom)
library(captioner)
library(cowplot)
```

```{r loadingdata, echo=F, message=F, results='hide'}
data(diamonds)
```

# Abstract
Diamonds are no one's friend.

# Introduction

Sweeping generalizations have been made about the French [@RStudio].
How many diamonds would it take to have the equivalent value of one best friend?

# Methods

We compared assertaions made in a popular pop song to the `diamonds` dataset. 

$$\sum_{x=1}^Nicole Kidman + \frac{\delta(x)}{x}$$

# Results

```{r}
ggplot(diamonds, aes(carat, price, color=clarity))+
  geom_point()+
  theme_cowplot()+
  labs(x = "Carat", y = "Price")
```
```{r, echo=F}
mod <- lm(price ~ carat, data=diamonds)

kable(tidy(mod), digits = 2)
```

This is how many diamonds it takes: `r mod$coefficients["carat"][[1]]`


# Discussion

This is clearly an inordinate number of diamonds.

# References